Supplementary Material for Asymmetry paper

### 2020-05-14 Supplementary/Sup_mat.Rmd
Added Discussion Heading  for Exp4
new version of sup mat

```{r drawdistributions, include = T, echo = F, fig.height = 2, fig.cap="_The left hand plot shows a histrogram for the empirical data from @clarke2015failure with a line to show a beta distribution that had been fit to these data. The right hand plot shows how this distribution would change had the participants' mean position had been biased towards one of the side hoops to varying degrees._", fig.align = 'center'}
load("../power/Hoop_size/scratch/sampled_data")
load("../power/Hoop_size/scratch/df_part2")

@@

The fit with the empirical data is reasonable, although we under-estimate the frequency of standing positions $\phi\approx0.5$, in this case 0.5 is considered the central point with 0 and 1 representing the left and right hoop respectively. We assumed that by introducing a difference in size between the two hoops that this distribution would shift towards the smaller hoop so as to balance their chances of success. We assumed that the difference in hoop size would cause particiapnts to stand slightly closer to the small hoop, in this case the shift in mean would be +0.05.

@@

@@

>>>>

```{r drawdistributions, include = T, echo = F, fig.height = 2, fig.cap="_The left hand plot shows a histrogram for the empirical data from @clarke2015failure with a line to show a beta distribution that had been fit to these data. The right hand plot shows how this distribution would change had the participants' mean position had been biased towards one of the side hoops to varying degrees._", fig.align = 'center'}
# load("../power/Hoop_size/scratch/sampled_data")
load("../power/Hoop_size/scratch/df_part2")

@@

The fit with the empirical data is reasonable, although we under-estimate the frequency of standing positions $\phi\approx0.5$, in this case 0.5 is considered the central point with 0 and 1 representing the left and right hoop respectively. We assumed that by introducing a difference in size between the two hoops that this distribution would shift towards the smaller hoop so as to balance their chances of success. We assumed that the difference in hoop size would cause particiapnts to stand slightly closer to the small hoop, in this case the shift in mean would be +0.05. 
```{r Hoop Size resampling, include = T, echo = F}
# setup loop
n_iter <- 5000
n_subs <- seq(3, 24, 1)
n_trials <- 72

# for data.table
n <- n_iter * length(n_subs) * length(mu2) * length(n_trials)
df_sample <- data.table::data.table(iter = rep(0, n),
                                    n_subs = rep(0, n),
                                    n_trials = rep(0, n),
                                    difference = rep(0, n),
                                    baseline = rep(0, n),
                                    comparison = rep(0, n))

# loop for sampling
count <- 0
for(ii in 1:n_iter){
  base_shape <- get_shape_beta(mu1, var1)
  base_alpha <- base_shape$alpha
  base_beta <- base_shape$beta
  for(trials in n_trials){
    for(diff in mu2){
      comp_shape <- get_shape_beta(mu1 + diff, var1)
      comp_alpha <- comp_shape$alpha
      comp_beta <- comp_shape$beta
      for(sub in n_subs){
        # up count here
        count <- count + 1
        base_sample <- c()
        comp_sample <- c()
        for(s in 1:sub){
          base_sample <- c(base_sample, rbeta(n_trials, base_alpha, base_beta))
          comp_sample <- c(comp_sample, rbeta(n_trials, comp_alpha, comp_beta))
        }
        # df_sample <- rbind(df_sample, tibble(iter = ii,
        #                                      n_subs = sub,
        #                                      n_trials = trials,
        #                                      difference = diff,
        #                                      baseline = mean(base_sample),
        #                                      comparison = mean(comp_sample)))
        # add to table
        df_sample[count, iter := ii]
        df_sample[count, n_subs := sub]
        df_sample[count, n_trials := trials]
        df_sample[count, difference := diff]
        df_sample[count, baseline := mean(base_sample)]
        df_sample[count, comparison := mean(comp_sample)]
      }
    }
  }
}

@@

*What about the split in reward???*

@@

## Discussion
